# Academic Supervision

\begingroup
\fontfamily{ppl}\fontsize{12}{16}\selectfont\color{darktext}
MSc: 
\fontfamily{ppl}\fontsize{9}{16}\selectfont
S. Christianto \bullet 
H. Do \bullet 
B. Huerta \bullet
J. Lutum \bullet
A. Mondragon \bullet 
A. Krause \bullet 
L. Netter \bullet
T. Sandmann 
\endgroup


# Academic Tutoring

\begingroup
\fontfamily{ppl}\fontsize{12}{16}\selectfont\color{darktext}
PhD: 
\fontfamily{ppl}\fontsize{9}{16}\selectfont
O. Burbano-Figueroa \bullet
E. Fernandez \bullet
A. Krause \bullet 
I. Liman \bullet 
G. Luu \bullet 
A. Mya Mon \bullet
W. Oluoch \bullet
M. Ruett \bullet
N. Sulaiman \bullet
N. Yigzaw 
\endgroup
    
\begingroup
\fontfamily{ppl}\fontsize{12}{16}\selectfont\color{darktext}
MSc: 
\fontfamily{ppl}\fontsize{9}{16}\selectfont
D. Ahebwe (MSc) \bullet
D. Bastakoti (MSc) \bullet
H. Mufumbiro (MSc) \bullet
P. Phyo Hein (MSc) \bullet
G. Rojas (MSc)
\endgroup
    

# Teaching

```{r}
tribble(
  ~ Date, ~ Role, ~ CourseDepartmentUniversity, ~ Place,
  
  "2018 to Present", 
  "Lecturer, Modelling \u2022 Crop Systems Analysis \u2022 Decision Analysis", 
  "Department of Horticultural Sciences/ ARTS Masters programs, INRES, University of Bonn, Germany \u2022 4 semester week hours of lectures", 
  "",

"2018 to Present",
"Lecturer, Academic Writing \u2022 Introduction to R \u2022 Interdisciplinary research \u2022 Complex Systems Modelling",
  "The Bonn International Graduate School for Development Research, Center for Development Research, University of Bonn, Germany \u2022 15 lectures a year", 
"",

"2019",
"Invited Lecturer, Introduction to R \u2022 Ethnobotany research and modelling",
  "Kunming Institute of Botany, Yunnan, China", 
"",

  "2014 to 2015", 
  "Invited Lecturer, Sustainable Agricultural Production Systems", 
  "Faculty of Life Sciences, Rhine Waal University of Applied Sciences, Germany \u2022 3 lectures a year", 
  "",

  "2014", 
  "Invited Field Course Instructor, Mabira Forest Biodiversity Assessment", 
  "College of Agricultural and Environmental Sciences, Makerere University, Uganda", 
"",

"2002",
 "Professor’s Assistant",
 "Japanese Sustainable Systems, Sterling College, Vermont/ Hokkaido, Japan",
"",) %>% 
  #detailed_entries(data, what, when, with, where, why, .protect = TRUE)
  detailed_entries(CourseDepartmentUniversity, Place, Role, Date)
```

\begingroup
\fontfamily{ppl}\fontsize{14}{16}\selectfont\color{darktext}
\textbullet Teaching outside academia
\endgroup

```{r}
tribble(
  ~ Date, ~ Role, ~ CourseDepartmentUniversity, ~ Place,
  
  "2006 to 2007", 
  "Instructor/ Mate/ Captain, Maritime Outdoor Education Programs", 
  "Call of the Sea, Sailing School Vessel (SSV) Schooner Seaward \u2022 Sausalito, California American Sail Training Association, Fleet of Tall Ships", 
"",

  "2004 to 2006", 
  "Environmental Educator, Marine Biology and Outdoor Education", 
 "Tall-ship program, SSV Schooner Tole Mour, California, Catalina Island Marine Institute (CIMI)", 
"",

  "2003 to 2004", 
 "Educator, Maritime Based High School Programs", 
 "SSV Schooner Lettie G. Howard \u2022 New York, New York City Maritime Museum/ New York Harbor School", 
"",

 "2002 to 2003", 
 "Instructor, Outdoor Leadership", 
"Hurricane Island Outward Bound School, Maine", 
"",

) %>% 
  #detailed_entries(data, what, when, with, where, why, .protect = TRUE)
  detailed_entries(CourseDepartmentUniversity, Place, Role, Date)
```

# Co-Supervised Theses

```{r}
tribble(
  ~ Date, ~ Role, ~ CourseDepartmentUniversity, ~ Place,
  
  "2022", 
  "B. Huerta. MSc Thesis, University of Bonn, Germany", 
  "The effect of agricultural management practices on aflatixin reduction in maize in Mexico - a Decision Analysis approach (co-supervisor with Prof. Dr. Eike Luedeling)", 
"",

    "2022", 
  "A. Krause. MSc Thesis, University of Bonn, Germany", 
  "Factors influencing rural farm women’s empowerment in agricultural development (co-supervisor with Prof. Dr. Eike Luedeling)", 
"",

 "2020", 
  "J. Lutum. MSc Thesis, University of Bonn, Germany", 
  "A decision analysis approach to support cover crop selection in the Lower Rhine region (co-supervisor with Prof. Dr. Eike Luedeling)", 
"",

  "2020", 
  "L. Netter. MSc Thesis, University of Bonn, Germany", 
  "Agroforestry and restoration with the Gold Standard - Decision Analysis of a voluntary carbon offset label (co-supervisor with Prof. Dr. Eike Luedeling)", 
"",

  "2020", 
  "T. Sandmann. MSc Thesis, University of Bonn, Germany", 
  "Urban Agriculture in a Changing Climate -
An Evidence Gap Map  (co-supervisor with Prof. Dr. Eike Luedeling)", 
"",

 "2020", 
  "S. Christianto. MSc Thesis, University of Bonn, Germany", 
  "Assessing Profitability in Intervention of Agroforestry in Indonesia (co-supervisor with Prof. Dr. Eike Luedeling)", 
"",

  "2019", 
  "H. Do. MSc Thesis, University of Bonn, Germany", 
  "Helping farmers choose — Probabilistic modelling of agroforestry options in Northern Vietnam (co-supervisor with Prof. Dr. Eike Luedeling)", 
"",

) %>% 
  #detailed_entries(data, what, when, with, where, why, .protect = TRUE)
  detailed_entries(CourseDepartmentUniversity, Place, Role, Date)
```


